---
title: "Nike Brand Intelligence: Text Analytics for Strategic Decision-Making"
subtitle: "Data & AI Consulting Team Report"
author: "Valentine_Dube"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)
```

# Executive Summary

**Client:** Nike Inc. - Chief Marketing Officer & VP of Consumer Insights

**Business Challenge:** Nike leadership has observed increasing online conversation around sustainability, mixed sentiment about pricing, strong engagement with product drops, and growing competition from challenger brands. They commissioned our team to answer: *"What are customers really saying about Nike — and how should we respond strategically?"*

**Data Collected:** Multi-channel customer feedback corpus including Nike.com product reviews, YouTube sneaker comparison videos, social media reactions, and Reddit authenticity discussions.

# 1. Business Context & Objectives

## 1.1 Strategic Questions Addressed

This analysis focuses on four critical business questions requested by Nike leadership:

1. How is Nike emotionally positioned in online conversations?
2. What complaints drive negative reviews of specific product lines?
3. Is Nike's sustainability messaging resonating with customers?
4. Are customers increasingly describing Nike as overpriced?

## 1.2 Known Limitations

- Sampling Bias
- Fake Review Risk
- Lexicon Bias
- Cultural Context
- Temporal Limitation

# 2. Technical Setup & Data Loading

## 2.1 Loading Required Packages

```{r load_packages}
# Core tidyverse packages
library(tidyverse)
library(tidytext)
library(stringr)

# Text processing
library(tm)
library(SnowballC)
library(textdata)

# Topic modeling
library(topicmodels)

# Network visualization
library(igraph)
library(ggraph)

# Utilities
library(scales)
library(pdftools)

# Load stop words
data(stop_words)
```

# Part A: Data Collection and Cleaning

## Intro

This analysis uses real Nike customer feedback collected from Reddit sneaker communities (r/Sneakers, r/Nike, r/running). Data was compiled from threads discussing Nike product quality, comfort, pricing, and brand perception.

```{r data_loading}


# load data
file_path <- "C:/Users/valen/Downloads/Nike_merged_2 (1).pdf"

# Read PDF text
pdf_pages <- pdftools::pdf_text(file_path)

# Combine all pages into one string
full_text <- paste(pdf_pages, collapse = "\n")

# Split into individual comments/reviews
lines <- str_split(full_text, "\n")[[1]]

# Create raw dataframe
nike_raw <- tibble(comment = lines)

# Data Cleaning: remove empty lines, headers, and very short fragments
nike_raw <- nike_raw %>%
  mutate(comment = str_squish(comment)) %>%
  filter(comment != "") %>%
  filter(!str_detect(comment, "^\\d+$")) %>%
  filter(!comment %in% c("Reply", "1 year ago", "YOUTUBE NIKE REVIEWS")) %>%
  filter(str_length(comment) >= 20)

# Add document ID for tracking
nike_raw <- nike_raw %>%
  mutate(doc_id = row_number())

# Data Preview
print(head(nike_raw, 20))
cat("\n")
cat("========== DATA COLLECTION SUMMARY ==========\n")
cat("Total number of Nike customer reviews/comments:", nrow(nike_raw), "\n")
cat("Average comment length (characters):", round(mean(nchar(nike_raw$comment)), 1), "\n")
cat("Median comment length (characters):", median(nchar(nike_raw$comment)), "\n")
cat("Longest comment:", max(nchar(nike_raw$comment)), "characters\n")
cat("Shortest comment:", min(nchar(nike_raw$comment)), "characters\n\n")

cat("Data sources:\n")
cat("  - Nike.com product reviews (Metcon, Jordan 9, running shoes)\n")
cat("  - YouTube sneaker review comments (comfort comparisons, brand discussions)\n")
cat("  - Social media discussions (Instagram, TikTok Nike posts)\n")
cat("  - Reddit sneaker communities (authenticity, durability experiences)\n")
cat("Collection period: Q4 2023 - Q1 2024\n")
cat("=============================================\n")
```

# Part B: Text Processing

## Tokenization and Cleaning

```{r text_processing}


# Tokenize into words
tidy_words <- nike_raw %>%
  unnest_tokens(word, comment)

# Remove stop words
tidy_words_clean <- tidy_words %>%
  anti_join(stop_words, by = "word")

# Filter out numbers and non-alphabetic tokens
tidy_words_clean <- tidy_words_clean %>%
  filter(str_detect(word, "[a-z]")) %>%
  filter(!str_detect(word, "^\\d+$"))

# Stemming
tidy_words_clean <- tidy_words_clean %>%
  mutate(word_stem = SnowballC::wordStem(word))

print(head(tidy_words_clean, 25))
cat("Total tokens after cleaning:", nrow(tidy_words_clean), "\n")
```

## Preprocessing Decisions

Stop word removal eliminated common filler words to focus on meaningful content words.

Stemming reduced related words to their root form.

The original `word` column was kept alongside `word_stem` for readable outputs.

## Word Frequency Analysis

```{r word_frequency}
# load libraries
library(topicmodels)
library(igraph)
library(ggraph)
library(ggplot2)

# Count word frequencies
word_freq <- tidy_words_clean %>%
  count(word, sort = TRUE)

print(head(word_freq, 30))

# Visualize top 25 words
word_freq %>%
  slice_max(n, n = 25) %>%
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Top 25 Most Frequent Words in Nike Customer Reviews",
    subtitle = "Stop words removed",
    x = "Word",
    y = "Frequency"
  ) +
  theme_minimal()
```

# Part C: N-Gram Analysis

## Bigram Extraction and Cleaning

```{r bigrams}
# Extract bigrams
bigrams <- nike_raw %>%
  unnest_tokens(bigram, comment, token = "ngrams", n = 2)

# Separate into word1 and word2
bigrams_separated <- bigrams %>%
  separate(bigram, into = c("word1", "word2"), sep = " ", fill = "right")

# Remove stop words from both positions
bigrams_filtered <- bigrams_separated %>%
  filter(!is.na(word1), !is.na(word2)) %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word) %>%
  filter(str_detect(word1, "[a-z]"),
         str_detect(word2, "[a-z]"))

# Count bigram frequencies
bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)

print(head(bigram_counts, 30))
```

## Bigram Visualization

```{r bigram_viz}
bigram_counts %>%
  mutate(bigram = paste(word1, word2)) %>%
  slice_max(n, n = 20) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = "darkred") +
  coord_flip() +
  labs(
    title = "Top 20 Bigrams in Nike Customer Reviews",
    subtitle = "Stop words removed | Reveals key phrase patterns",
    x = "Bigram",
    y = "Frequency"
  ) +
  theme_minimal()
```

# Part D: Sentiment Analysis

## Bing Sentiment

```{r bing_sentiment}
# Load Bing lexicon
bing_lex <- tidytext::get_sentiments("bing")

# Join words with sentiment labels
bing_sentiment <- tidy_words_clean %>%
  inner_join(bing_lex, by = "word")

# Count positive vs. negative words
bing_results <- bing_sentiment %>%
  count(sentiment, sort = TRUE)

print(bing_results)

# Visualize
ggplot(bing_results, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_col() +
  scale_fill_manual(values = c("negative" = "tomato", "positive" = "seagreen")) +
  labs(
    title = "Bing Sentiment: Positive vs. Negative Word Count",
    x = "Sentiment",
    y = "Word Count"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## AFINN Sentiment

```{r afinn_sentiment}
# Load AFINN lexicon
afinn_lex <- tidytext::get_sentiments("afinn")

# Join and calculate scores
afinn_sentiment <- tidy_words_clean %>%
  inner_join(afinn_lex, by = "word")

# Overall sentiment score
afinn_score <- afinn_sentiment %>%
  summarise(
    total_afinn_score = sum(value),
    avg_afinn_score = mean(value),
    median_afinn_score = median(value)
  )

print(afinn_score)

# Document-level AFINN scores
afinn_by_doc <- tidy_words_clean %>%
  inner_join(afinn_lex, by = "word") %>%
  group_by(doc_id) %>%
  summarise(afinn_doc_score = sum(value), .groups = "drop")

# Distribution of document scores
ggplot(afinn_by_doc, aes(x = afinn_doc_score)) +
  geom_histogram(binwidth = 1, fill = "dodgerblue", color = "white") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 1) +
  labs(
    title = "Distribution of Document-Level Sentiment Scores (AFINN)",
    x = "AFINN Sentiment Score",
    y = "Number of Reviews"
  ) +
  theme_minimal()
```

## NRC Emotion Breakdown

```{r nrc_sentiment}
# Load NRC lexicon
nrc_lex <- tidytext::get_sentiments("nrc")

# Join words with emotions
nrc_sentiment <- tidy_words_clean %>%
  inner_join(nrc_lex, by = "word")

# Count emotions
nrc_results <- nrc_sentiment %>%
  count(sentiment, sort = TRUE)

print(nrc_results)

# Visualize emotions
ggplot(nrc_results, aes(x = reorder(sentiment, n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(
    title = "NRC Emotion Breakdown: What Emotions Do Customers Express?",
    x = "Emotion",
    y = "Word Count"
  ) +
  theme_minimal()
```

## Comment-Level Sentiment Classification

```{r comment_sentiment}
# Calculate Bing net score per comment (+1 for positive, -1 for negative)
bing_by_doc <- tidy_words_clean %>%
  inner_join(bing_lex, by = "word") %>%
  mutate(score = ifelse(sentiment == "positive", 1, -1)) %>%
  group_by(doc_id) %>%
  summarise(net_bing_score = sum(score), .groups = "drop")

# Join back to original comments
nike_comments_scored <- nike_raw %>%
  left_join(bing_by_doc, by = "doc_id") %>%
  mutate(
    net_bing_score = replace_na(net_bing_score, 0),
    sentiment_bucket = case_when(
      net_bing_score > 0  ~ "Positive",
      net_bing_score < 0  ~ "Negative",
      TRUE                ~ "Neutral"
    )
  )

print(head(nike_comments_scored, 20))

nike_comments_scored %>%
  count(sentiment_bucket) %>%
  ggplot(aes(x = sentiment_bucket, y = n, fill = sentiment_bucket)) +
  geom_col() +
  scale_fill_manual(values = c("Positive" = "seagreen", "Neutral" = "gray", "Negative" = "tomato")) +
  labs(
    title = "Comment-Level Sentiment Distribution",
    x = "Sentiment Bucket",
    y = "Number of Comments"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

# 6. Product-Level Sentiment Analysis

## 6.1 Identify Product Line Mentions

```{r product_mentions}
product_mentions <- nike_raw %>%
  mutate(product_line = case_when(
    str_detect(str_to_lower(comment), "\\bjordan\\b|jordan 1|jordan low") ~ "Jordan",
    str_detect(str_to_lower(comment), "air max") ~ "Air Max",
    str_detect(str_to_lower(comment), "air force|\\baf1\\b") ~ "Air Force 1",
    str_detect(str_to_lower(comment), "vomero") ~ "Vomero",
    str_detect(str_to_lower(comment), "pegasus") ~ "Pegasus",
    str_detect(str_to_lower(comment), "vapormax") ~ "Vapormax",
    str_detect(str_to_lower(comment), "\\bdunk\\b|dunks") ~ "Dunk",
    str_detect(str_to_lower(comment), "metcon") ~ "Metcon",
    str_detect(str_to_lower(comment), "cortez") ~ "Cortez",
    str_detect(str_to_lower(comment), "huarache") ~ "Huarache",
    str_detect(str_to_lower(comment), "killshot") ~ "Killshot",
    TRUE ~ "General Nike"
  ))

product_sentiment <- product_mentions %>%
  left_join(bing_by_doc, by = "doc_id") %>%
  mutate(net_bing_score = replace_na(net_bing_score, 0)) %>%
  group_by(product_line) %>%
  summarise(
    num_comments = n(),
    avg_sentiment = mean(net_bing_score),
    .groups = "drop"
  ) %>%
  filter(num_comments >= 2) %>%
  arrange(desc(avg_sentiment))

print(product_sentiment)

product_sentiment %>%
  ggplot(aes(x = reorder(product_line, avg_sentiment), y = avg_sentiment, fill = avg_sentiment > 0)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "seagreen", "FALSE" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Average Sentiment by Nike Product Line",
    x = "Product Line",
    y = "Average Bing Sentiment Score"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## 6.2 Deep Dive: Metcon 10 Training Shoe Analysis

```{r metcon_analysis}
metcon_reviews <- nike_raw %>%
  filter(str_detect(str_to_lower(comment), "metcon"))

cat("Number of Metcon reviews:", nrow(metcon_reviews), "\n\n")
print(head(metcon_reviews$comment, 10))
cat("\n")

metcon_themes <- metcon_reviews %>%
  mutate(
    sizing_issue = str_detect(str_to_lower(comment), "narrow|small|tight|half size|toe box|skinny"),
    comfort_positive = str_detect(str_to_lower(comment), "comfortable|comfy|comfort"),
    stability_positive = str_detect(str_to_lower(comment), "stable|stability|grounded"),
    flexibility_mention = str_detect(str_to_lower(comment), "flexible|flexibility|stiff|rigid"),
    price_concern = str_detect(str_to_lower(comment), "price|worth|full price"),
    design_critique = str_detect(str_to_lower(comment), "clunky|bulky|design|colour|color")
  )

metcon_theme_summary <- tibble(
  theme = c("Sizing Issues", "Comfort (Positive)", "Stability (Positive)",
            "Flexibility", "Price Concerns", "Design Critiques"),
  mentions = c(
    sum(metcon_themes$sizing_issue),
    sum(metcon_themes$comfort_positive),
    sum(metcon_themes$stability_positive),
    sum(metcon_themes$flexibility_mention),
    sum(metcon_themes$price_concern),
    sum(metcon_themes$design_critique)
  )
) %>%
  mutate(pct_of_metcon_reviews = round(mentions / nrow(metcon_reviews) * 100, 1))

print(metcon_theme_summary)

ggplot(metcon_theme_summary, aes(x = reorder(theme, mentions), y = mentions, fill = theme)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  geom_text(aes(label = paste0(mentions, " (", pct_of_metcon_reviews, "%)")),
            hjust = -0.1, size = 3.5) +
  labs(
    title = "Metcon 10 Review Themes",
    subtitle = "Sizing issues dominate customer feedback",
    x = "Theme",
    y = "Number of Mentions"
  ) +
  theme_minimal() +
  ylim(0, max(metcon_theme_summary$mentions) * 1.2)
```

# 7. Aspect-Based Sentiment

```{r aspect_flags}
aspect_data <- nike_raw %>%
  mutate(
    quality_flag = str_detect(str_to_lower(comment),
                              "quality|cheap|craftsmanship|glue|stitch|material|finish|peeling|trash|shoddy"),
    comfort_flag = str_detect(str_to_lower(comment),
                              "comfort|comfortable|cushion|support|arch|pain|hurt|stiff|soft|plush"),
    sizing_flag = str_detect(str_to_lower(comment),
                             "size|sizing|narrow|wide|tight|fit|small|large|toe box|run small|run big"),
    pricing_flag = str_detect(str_to_lower(comment),
                              "price|priced|expensive|overpriced|worth|value|afford|cheap|costly"),
    durability_flag = str_detect(str_to_lower(comment),
                                 "durable|durability|wore out|fall apart|separating|crack|sole|lasted|longevity"),
    design_flag = str_detect(str_to_lower(comment),
                             "design|style|look|colorway|clean|ugly|aesthetic|sleek|sharp"),
    sustainability_flag = str_detect(str_to_lower(comment),
                                     "sustainable|sustainability|recyclable|carbon|footprint|greenwashing|eco|environment")
  )

aspect_summary <- tibble(
  aspect = c("Quality", "Comfort", "Sizing", "Pricing", "Durability", "Design", "Sustainability"),
  mentions = c(
    sum(aspect_data$quality_flag),
    sum(aspect_data$comfort_flag),
    sum(aspect_data$sizing_flag),
    sum(aspect_data$pricing_flag),
    sum(aspect_data$durability_flag),
    sum(aspect_data$design_flag),
    sum(aspect_data$sustainability_flag)
  )
) %>%
  mutate(pct_of_corpus = round(mentions / nrow(nike_raw) * 100, 1))

print(aspect_summary)

ggplot(aspect_summary, aes(x = reorder(aspect, mentions), y = mentions, fill = aspect)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  geom_text(aes(label = paste0(mentions, " (", pct_of_corpus, "%)")), hjust = -0.1, size = 3.5) +
  labs(
    title = "Key Business Themes Mentioned in Nike Customer Reviews",
    x = "Aspect",
    y = "Number of Mentions"
  ) +
  theme_minimal() +
  ylim(0, max(aspect_summary$mentions) * 1.15)
```

# 8. Topic Modeling (LDA)

```{r lda_prep}
lda_input <- tidy_words_clean %>%
  count(doc_id, word) %>%
  group_by(word) %>%
  filter(sum(n) >= 5) %>%
  ungroup()

lda_dtm <- lda_input %>%
  cast_dtm(document = doc_id, term = word, value = n)

print(lda_dtm)
```

```{r lda_model}
k_topics <- 5

set.seed(1234)
lda_model <- LDA(lda_dtm, k = k_topics, control = list(seed = 1234))

lda_topics <- tidy(lda_model, matrix = "beta")

top_terms <- lda_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  arrange(topic, desc(beta))

print(top_terms)
```

```{r lda_viz}
top_terms %>%
  mutate(term = tidytext::reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free", ncol = 2) +
  coord_flip() +
  tidytext::scale_x_reordered() +
  labs(
    title = "LDA Topic Modeling: Top 10 Terms per Topic",
    x = "Term",
    y = "Beta"
  ) +
  theme_minimal()
```

# 9. TF-IDF by Product Line

```{r tfidf_product}
product_words <- tidy_words_clean %>%
  left_join(product_mentions %>% select(doc_id, product_line), by = "doc_id") %>%
  filter(product_line != "General Nike") %>%
  count(product_line, word, sort = TRUE)

product_tfidf <- product_words %>%
  bind_tf_idf(term = word, document = product_line, n = n) %>%
  arrange(desc(tf_idf))

print(head(product_tfidf, 30))

product_tfidf %>%
  group_by(product_line) %>%
  slice_max(tf_idf, n = 8) %>%
  ungroup() %>%
  mutate(word = tidytext::reorder_within(word, tf_idf, product_line)) %>%
  ggplot(aes(word, tf_idf, fill = product_line)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ product_line, scales = "free", ncol = 2) +
  coord_flip() +
  tidytext::scale_x_reordered() +
  labs(
    title = "TF-IDF: Distinctive Words by Nike Product Line",
    x = "Word",
    y = "TF-IDF Score"
  ) +
  theme_minimal()
```

# 10. Zipf's Law Verification

```{r zipf_law}
zipf_data <- tidy_words_clean %>%
  count(word, sort = TRUE) %>%
  mutate(
    rank = row_number(),
    term_frequency = n / sum(n)
  )

print(head(zipf_data, 20))

ggplot(zipf_data, aes(x = rank, y = term_frequency)) +
  geom_line(color = "steelblue", linewidth = 1) +
  scale_x_log10(labels = comma) +
  scale_y_log10(labels = comma_format(accuracy = 0.00001)) +
  labs(
    title = "Zipf's Law: Word Frequency vs Rank",
    x = "Rank (log scale)",
    y = "Term Frequency (log scale)"
  ) +
  theme_minimal()
```

# 11. Keyword Co-Occurrence Network

```{r cooccurrence_network}
cooccur_data <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE) %>%
  filter(n >= 8)

if (nrow(cooccur_data) > 0) {
  cooccur_graph <- graph_from_data_frame(cooccur_data)

  set.seed(123)
  ggraph(cooccur_graph, layout = "fr") +
    geom_edge_link(aes(edge_width = n), alpha = 0.4, color = "gray50") +
    geom_node_point(size = 4, color = "steelblue") +
    geom_node_text(aes(label = name), repel = TRUE, size = 3) +
    scale_edge_width(range = c(0.5, 2)) +
    labs(
      title = "Keyword Co-Occurrence Network",
      subtitle = "Words frequently appearing together in Nike reviews"
    ) +
    theme_void() +
    theme(legend.position = "none")
}
```

# 12. Sustainability Analysis

```{r sustainability_analysis}
sustainability_comments <- nike_raw %>%
  filter(str_detect(str_to_lower(comment), "sustainab|eco|green|carbon|footprint|recycle|environment"))

cat("Number of sustainability-related comments:", nrow(sustainability_comments), "\n")
cat("Percentage of total corpus:", round(nrow(sustainability_comments) / nrow(nike_raw) * 100, 2), "%\n\n")

greenwashing_comments <- nike_raw %>%
  filter(str_detect(str_to_lower(comment), "greenwash|green wash|fake eco"))

cat("Number of 'greenwashing' accusations:", nrow(greenwashing_comments), "\n\n")

eco_terms <- c("sustainable", "sustainability", "recyclable", "recycled", "carbon", "footprint",
               "eco-friendly", "environment", "green", "planet", "climate")

eco_search_results <- sapply(eco_terms, function(term) {
  sum(str_detect(str_to_lower(nike_raw$comment), term))
})

cat("Breakdown of eco-term appearances:\n")
print(eco_search_results)
```

# 13. Competitive Threat Analysis: Nike vs Adidas

```{r competitive_analysis}
adidas_mentions <- nike_raw %>%
  filter(str_detect(str_to_lower(comment), "adidas"))

cat("Number of comments mentioning Adidas:", nrow(adidas_mentions), "\n")
cat("Percentage of total corpus:", round(nrow(adidas_mentions) / nrow(nike_raw) * 100, 1), "%\n\n")

print(head(adidas_mentions$comment, 15))
cat("\n")

adidas_sentiment_categories <- adidas_mentions %>%
  left_join(nike_comments_scored %>% select(doc_id, sentiment_bucket), by = "doc_id") %>%
  mutate(
    adidas_positive = str_detect(str_to_lower(comment),
                                 "adidas better|switched to adidas|prefer adidas|adidas quality|adidas winning"),
    nike_defensive = str_detect(str_to_lower(comment),
                                "nike still|nike better|nike number 1|nike has"),
    price_comparison = str_detect(str_to_lower(comment),
                                  "adidas cheaper|adidas affordable|nike expensive|nike overpriced"),
    quality_comparison = str_detect(str_to_lower(comment),
                                    "adidas quality|adidas durable|nike quality|nike fell apart")
  )

comparison_summary <- tibble(
  comparison_type = c("Adidas Positive", "Nike Defensive", "Price Comparison", "Quality Comparison"),
  count = c(
    sum(adidas_sentiment_categories$adidas_positive, na.rm = TRUE),
    sum(adidas_sentiment_categories$nike_defensive, na.rm = TRUE),
    sum(adidas_sentiment_categories$price_comparison, na.rm = TRUE),
    sum(adidas_sentiment_categories$quality_comparison, na.rm = TRUE)
  )
)

print(comparison_summary)
```

# 14. Export Analysis Artifacts

```{r export_data}
write.csv(nike_raw, "nike_comments_raw.csv", row.names = FALSE)
write.csv(tidy_words_clean, "nike_words_clean.csv", row.names = FALSE)
write.csv(word_freq, "nike_word_frequency.csv", row.names = FALSE)
write.csv(bigram_counts, "nike_bigram_counts.csv", row.names = FALSE)
write.csv(nike_comments_scored, "nike_comments_scored.csv", row.names = FALSE)
write.csv(product_sentiment, "nike_product_sentiment.csv", row.names = FALSE)
write.csv(aspect_summary, "nike_aspect_summary.csv", row.names = FALSE)
write.csv(top_terms, "nike_lda_top_terms.csv", row.names = FALSE)
write.csv(product_tfidf, "nike_product_tfidf.csv", row.names = FALSE)

cat("Analysis artifacts exported successfully.\n")
```
